Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-14 analysis/paper/paper.Rmd
Automatically export figures as .eps when knitting to Word

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(fig.pos = "p")
knitr::opts_chunk$set(out.width = "100%", dpi = 300)
knitr::opts_chunk$set(fig.width = 3.31)
knitr::opts_chunk$set(fig.height = 3.31)
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)

@@

ggsave("./Figures/Sparks_Figure_1.eps", width = 84, height = 84, units = "mm")

@@

ggsave("./Figures/Sparks_Figure_2.eps", width = 84, height = 84, units = "mm")
```

@@

ggsave("./Figures/Sparks_Figure_3.eps", width = 84, height = 84, units = "mm")
```

>>>>

```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300
)

@@

@@

@@
